---
title: "Additional Information"
output:
  html_document:
    df_print: paged
---

<style type="text/css">
.main-container {
  max-width: 1250px;
  margin-left: auto;
  margin-right: auto;
}

 /* unvisited link */
a:link {
  color: navy;
}

/* visited link */
a:visited {
  color: green;
}

/* mouse over link */
a:hover {
  color: purple;
}

/* selected link */
a:active {
  color: blue;
} 
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-library, message=FALSE, echo=FALSE}
rm(list = ls())
pacman::p_load(tidyverse, rmarkdown, htmlwidgets, htmltools, maps, 
               webshot, leaflet, kableExtra, scales, stringr, stringi,
               mapproj, usmap, rvest, rcis, plotly, cowplot, socviz, 
               RColorBrewer, kableExtra, gridExtra, dplyr, tidyr, 
               ggplot2, diffpriv, sdcMicro, readr, ggrepel, randomNames, tidyquery, countrycode)

suppressPackageStartupMessages({
  library(data.table)
  library(digest)
  library(knitr) # used only for post creation
})

library(tinytex) 
webshot::install_phantomjs(force=TRUE)

library(DBI) # main DB interface
library(RSQLite) # To connect to SQLite DB
library(tidyverse) # for dplyr, readr etc.
library(dbplyr) # dplyr backend for DBs
```

The information in this study will be used only for research purposes and in ways that will not reveal the identies of people. Federal or state laws may require us to show information to university or government officials (or sponsors) who are responsible for monitoring the safety of this study. Directly identifying information (e.g. names, addresses) will be safeguarded and maintained under controlled conditions. People will not be identified in any publication from this study. For (even) more information, please scroll to the bottom of the page for a summary of the datasets.

```{r, message = FALSE, echo=FALSE}
# read in the TidyTuesday dataset
#library(htmltools)
rawData1_1 <- read.csv("data/MockData4.csv")

# columns which will be changed
willAnonymize <- c("email", "city")

# anonymize using the murmur32 algorithm 
anonymize <- function(x, algo="murmur32"){
  unq_hashes <- vapply(unique(x), function(object) digest(object, algo=algo), 
                       FUN.VALUE="", USE.NAMES=TRUE) #hashing for unique inputs
  unname(unq_hashes[x])
}

# columns which will be changed
willAnonymize2 <- c("name", "ssn")

# anonymize using the xxhash64 algorithm 
anonymize2 <- function(x, algo="xxhash64"){
  unq_hashes2 <- vapply(unique(x), function(object) digest(object, algo=algo), 
                       FUN.VALUE="", USE.NAMES=TRUE) #hashing for unique inputs
  unname(unq_hashes2[x])
}

rawData1_2 <- rawData1_1 # create a new dataframe from changed data of 1/0

# change age format --> re-coding the age to reduce uniqueness //
# generalization to achieve k-anonymity
rawData1_2$age <- cut(rawData1_2$age, breaks = c(0, 21, 35, 49, 59, 71, 100))

setDT(rawData1_2) #turning the dataframe into a data table to 
# be able to use the := function

# anonymize the data// run the dataset through the anonymize functions
rawData1_2[, (willAnonymize) := lapply(.SD, anonymize), .SDcols = willAnonymize]
rawData1_2[, (willAnonymize2) := lapply(.SD, anonymize2), .SDcols = willAnonymize2]

shuffled_data1_2 = rawData1_2[sample(1:nrow(rawData1_2)), ]

####################### CHANGING THE INFORMATION TO 1/0 #######################
# Diabetes
shuffled_data1_2$diabetes [shuffled_data1_2$diabetes == "Yes"] <- 1
shuffled_data1_2$diabetes [shuffled_data1_2$diabetes == "No"] <- 0
shuffled_data1_2$diabetes <- as.character(shuffled_data1_2$diabetes)

# Asthma
shuffled_data1_2$asthma [shuffled_data1_2$asthma == "Yes"] <- 1
shuffled_data1_2$asthma [shuffled_data1_2$asthma == "No"] <- 0
shuffled_data1_2$asthma <- as.character(shuffled_data1_2$asthma)

# Depression
shuffled_data1_2$depression [shuffled_data1_2$depression == "Yes"] <- 1
shuffled_data1_2$depression [shuffled_data1_2$depression == "No"] <- 0
shuffled_data1_2$depression <- as.character(shuffled_data1_2$depression)

# Anxiety
shuffled_data1_2$anxiety [shuffled_data1_2$anxiety == "Yes"] <- 1
shuffled_data1_2$anxiety [shuffled_data1_2$anxiety == "No"] <- 0
shuffled_data1_2$anxiety <- as.character(shuffled_data1_2$anxiety)

# Migraines
shuffled_data1_2$migraines [shuffled_data1_2$migraines == "Yes"] <- 1
shuffled_data1_2$migraines [shuffled_data1_2$migraines == "No"] <- 0
shuffled_data1_2$migraines <- as.character(shuffled_data1_2$migraines)

# Arthritis
shuffled_data1_2$arthritis [shuffled_data1_2$arthritis == "Yes"] <- 1
shuffled_data1_2$arthritis [shuffled_data1_2$arthritis == "No"] <- 0
shuffled_data1_2$arthritis <- as.character(shuffled_data1_2$arthritis)

# Eczema
shuffled_data1_2$eczema [shuffled_data1_2$eczema == "Yes"] <- 1
shuffled_data1_2$eczema [shuffled_data1_2$eczema == "No"] <- 0
shuffled_data1_2$eczema <- as.character(shuffled_data1_2$eczema)

# Stroke
shuffled_data1_2$stroke [shuffled_data1_2$stroke == "Yes"] <- 1
shuffled_data1_2$stroke [shuffled_data1_2$stroke == "No"] <- 0
shuffled_data1_2$stroke <- as.character(shuffled_data1_2$stroke)

# Dementia
shuffled_data1_2$dementia [shuffled_data1_2$dementia == "Yes"] <- 1
shuffled_data1_2$dementia [shuffled_data1_2$dementia == "No"] <- 0
shuffled_data1_2$dementia <- as.character(shuffled_data1_2$dementia)

# HIV
shuffled_data1_2$HIV [shuffled_data1_2$HIV == "Yes"] <- 1
shuffled_data1_2$HIV [shuffled_data1_2$HIV == "No"] <- 0
shuffled_data1_2$HIV <- as.character(shuffled_data1_2$HIV)

ID <- shuffled_data1_2$id
Gender <- shuffled_data1_2$gender
Location <- shuffled_data1_2$state
Race <- shuffled_data1_2$race

#original file is dat // changing the names 
shuffled_data1_2 <- shuffled_data1_2 %>%
  rename("ID" = id) %>%
  rename("Name" = name) %>%
  rename("Email" = email) %>%
  rename("Gender" = gender) %>%
  rename("Age" = age) %>%
  rename("City" = city) %>%
  rename("State" = state) %>%
  rename("SSN" = ssn) %>%
  rename("Race/Ethnicity" = race) %>%
  rename("Diabetes" = diabetes) %>%
  rename("Asthma" = asthma) %>%
  rename("Depression" = depression) %>% 
  rename("Anxiety" = anxiety) %>%
  rename("Migraines" = migraines) %>%
  rename("Arthritis" = arthritis) %>%
  rename("Eczema" = eczema) %>%
  rename("Stroke" = stroke) %>%
  rename("Dementia" = dementia) %>%
  rename("HIV" = HIV) 

write.csv(shuffled_data1_2,"data/anonymizedData.csv", row.names = FALSE)

shuffled_data1_3 <- read_csv("data/anonymizedData.csv")
# 
# shuffled_data1_3 <- shuffled_data1_3 %>%
#   select(Gender, Age, State,  `Race/Ethnicity`)
```

```{r noise-nd-1, warning=FALSE, message=TRUE, echo = FALSE}
# creating vectors, calling it to x
Diabetesx_20  <- shuffled_data1_3$Diabetes 
Asthmax_20  <- shuffled_data1_3$Asthma 
Depressionx_20  <- shuffled_data1_3$Depression 
Anxietyx_20  <- shuffled_data1_3$Anxiety 
Migrainesx_20  <- shuffled_data1_3$Migraines
Arthritisx_20  <- shuffled_data1_3$Arthritis 
Eczemax_20  <- shuffled_data1_3$Eczema 
Strokex_20  <- shuffled_data1_3$Stroke
Dementiax_20  <- shuffled_data1_3$Dementia 
HIVx_20  <- shuffled_data1_3$HIV 

# adding noise to 20% percent of the data
x_noise_20a <- sample(0:1, 200,replace=TRUE)
x_noise_20b <- sample(0:1, 200,replace=TRUE)
x_noise_20c <- sample(0:1, 200,replace=TRUE)
x_noise_20d <- sample(0:1, 200,replace=TRUE)
x_noise_20e <- sample(0:1, 200,replace=TRUE)
x_noise_20f <- sample(0:1, 200,replace=TRUE)
x_noise_20g <- sample(0:1, 200,replace=TRUE)
x_noise_20h <- sample(0:1, 200,replace=TRUE)
x_noise_20i <- sample(0:1, 200,replace=TRUE)
x_noise_20j <- sample(0:1, 200,replace=TRUE)

# about 20% of x has been corrupted // the first 200 values
Diabetesx_20[1:200] <- c(x_noise_20a)
Asthmax_20[1:200]  <- c(x_noise_20b)
Depressionx_20[1:200] <- c(x_noise_20c)
Anxietyx_20[1:200]  <- c(x_noise_20d)
Migrainesx_20[1:200] <- c(x_noise_20e)
Arthritisx_20[1:200]  <- c(x_noise_20f)
Eczemax_20[1:200]  <- c(x_noise_20g)
Strokex_20[1:200]  <- c(x_noise_20h)
Dementiax_20[1:200]  <-c(x_noise_20i)
HIVx_20[1:200]  <-  c(x_noise_20j)

# creating vectors, calling it to x
Diabetesx_20  <- Diabetesx_20 %>%
    as.character()
Asthmax_20  <- Asthmax_20 %>%
    as.character()
Depressionx_20  <- Depressionx_20 %>%
    as.character()
Anxietyx_20  <- Anxietyx_20 %>%
    as.character()
Migrainesx_20  <- Migrainesx_20 %>%
    as.character()
Arthritisx_20  <- Arthritisx_20 %>%
    as.character()
Eczemax_20  <- Eczemax_20 %>%
    as.character()
Strokex_20  <- Strokex_20 %>%
    as.character()
Dementiax_20  <- Dementiax_20 %>%
    as.character()
HIVx_20  <- HIVx_20 %>%
    as.character()

ID <- shuffled_data1_3$ID
Name <- shuffled_data1_3$Name
Email <- shuffled_data1_3$Email
Gender <- shuffled_data1_3$Gender
Age <- shuffled_data1_3$Age
City <- shuffled_data1_3$City
State <- shuffled_data1_3$State
SSN <- shuffled_data1_3$SSN
`Race/Ethnicity` <- shuffled_data1_3$`Race/Ethnicity`

shuffled_data1_4 <- tibble(ID, Name, Email, Gender, Age, City, State, SSN, `Race/Ethnicity`, Diabetesx_20, Asthmax_20, Depressionx_20, Anxietyx_20, Migrainesx_20, Arthritisx_20, Eczemax_20, Strokex_20, Dementiax_20, HIVx_20)

#original file is dat // changing the names 
shuffled_data1_4 <- shuffled_data1_4 %>%
  rename("Diabetes" = Diabetesx_20) %>%
  rename("Asthma" = Asthmax_20) %>%
  rename("Depression" = Depressionx_20) %>% 
  rename("Anxiety" = Anxietyx_20) %>%
  rename("Migraines" = Migrainesx_20) %>%
  rename("Arthritis" = Arthritisx_20) %>%
  rename("Eczema" = Eczemax_20) %>%
  rename("Stroke" = Strokex_20) %>%
  rename("Dementia" = Dementiax_20) %>%
  rename("HIV" = HIVx_20) 

write.csv(shuffled_data1_4,"data/anonymized2Data.csv", row.names = FALSE)
```


```{r, message = FALSE, echo=FALSE}
transit_cost <- readr::read_csv(glue::glue("data/anonymized2Data.csv")) %>%
  select(Gender, Age, State,  `Race/Ethnicity`)

transit_cost2 <-readr::read_csv(glue::glue("data/anonymized2Data.csv")) %>%
  select(Gender, Age, State,  `Race/Ethnicity`, Diabetes, Asthma, Depression, Anxiety, Migraines, Arthritis, Eczema, Stroke, Dementia, HIV)
# 
# transit_cost %>%
#   DT::datatable(list(scrollX = TRUE,
#                      pageLength = 50))
```


```{r, message = FALSE, echo=FALSE}
# Make a connection to a non-existant
# DB - here the DB `ticket_to_ride` does
# not yet exist.
# This step creates it.
con <- DBI::dbConnect(RSQLite::SQLite(), 
        dbname = "DP.sqlite")

```

```{r, message = FALSE, echo=FALSE}
# Write dataframes into DB tables 
dbWriteTable(con,
    "transit_cost", # table will be named transit_cost
    transit_cost, # df being written
    overwrite = TRUE)

dbWriteTable(con,
    "transit_cost2", # table will be named transit_cost
    transit_cost2, # df being written
    overwrite = TRUE)

# close the connection
dbDisconnect(con)
```

```{r, message = FALSE, echo=FALSE}
# Make a connection
ttr_con <- dbConnect(RSQLite::SQLite(), "DP.sqlite")
ttr_con2 <- dbConnect(RSQLite::SQLite(), "DP.sqlite")
# List tables in DB
# dbListTables(ttr_con)
```

<p>&nbsp;</p>

# Healthcare Dataset Results 
## Summary {.tabset .tabset-dropdown} 

<!-- The tables below break down the data collected from the data with 20% noise.  -->
Key: 0 represents the patient(s) have tested negative. In the tables, 1 refers to patient(s) testing positive.

### Total Patients for Each State
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using the connection reach into the DB
# and show some of the data
# Equivalent to:
#   SELECT * FROM transit_cost ...
tbl(ttr_con, "transit_cost") %>%
  count(State) %>%
  rename("Total" = n)
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients for Each State Based on Age Group
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con, "transit_cost") %>%
  count(State, Age) %>%
  rename("Total" = n)
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients Based on Age Group
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con, "transit_cost") %>%
  count(Age) %>%
  rename("Total" = n)
```
<p>&nbsp;</p><p>&nbsp;</p>

## Based on Condition and State {.tabset .tabset-dropdown} 
<!-- The tables below break down the data collected from the data with 20% noise.  -->
Note: 0 represents Negative, and 1 represents Positive.

### Total Patients with Diabetes
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(State, Diabetes) %>%
  rename("Total" = n)
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Asthma
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(State, Asthma) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Depression
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(State, Depression) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Anxiety
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(State, Anxiety) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Migraines
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(State, Migraines) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Arthritis
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost....
tbl(ttr_con2, "transit_cost2") %>%
  count(State, Arthritis) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Eczema
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(State, Eczema) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Stroke
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(State, Stroke) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Dementia
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(State, Dementia) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with HIV
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(State, HIV) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>


## Based on Condition and Gender{.tabset .tabset-dropdown} 
<!-- The tables below break down the data collected from the data with 20% noise.  -->
Note: 0 represents Negative, and 1 represents Positive.

### Total Patients with Diabetes
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, Diabetes) %>%
  rename("Total" = n)
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Asthma
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, Asthma) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Depression
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, Depression) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Anxiety
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, Anxiety) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Migraines
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, Migraines) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Arthritis
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, Arthritis) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Eczema
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, Eczema) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Stroke
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, Stroke) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Dementia
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, Dementia) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with HIV
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Gender, HIV) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

## Based on Condition and Age Group{.tabset .tabset-dropdown} 
<!-- The tables below break down the data collected from the data with 20% noise.  -->
Note: 0 represents Negative, and 1 represents Positive.

### Total Patients with Diabetes
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Diabetes) %>%
  rename("Total" = n)
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Asthma
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Asthma) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Depression
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Depression) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Anxiety
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Anxiety) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Migraines
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Migraines) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Arthritis
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Arthritis) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Eczema
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Eczema) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Stroke
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Stroke) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Dementia
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Dementia) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with HIV
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, HIV) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>


## Based on Condition, Age Group, and Gender{.tabset .tabset-dropdown} 
<!-- The tables below break down the data collected from the data with 20% noise.  -->
Note: 0 represents Negative, and 1 represents Positive.

### Total Patients with Diabetes
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender, Diabetes) %>%
  rename("Total" = n)
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Asthma
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender, Asthma) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Depression
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender,  Depression) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Anxiety
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost ...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender,  Anxiety) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Migraines
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender,  Migraines) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Arthritis
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost..
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender,  Arthritis) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Eczema
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost..
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender,  Eczema) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Stroke
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost..
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender,  Stroke) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with Dementia
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost..
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender,  Dementia) %>%
  rename("Total" = n) 
```
<p>&nbsp;</p><p>&nbsp;</p>

### Total Patients with HIV
```{r, message = FALSE, echo=FALSE}
# Get a glimpse of the data
# Using our connection reach into the DB
# and show us some of the data for GR
# Equivalent to:
#   SELECT * FROM transit_cost...
tbl(ttr_con2, "transit_cost2") %>%
  count(Age, Gender,  HIV) %>%
  rename("Total" = n) 

```

## Search
```{r, message = FALSE, echo=FALSE}
transit_cost %>%
  DT::datatable(list(scrollX = TRUE,
                     pageLength = 50))
```

## Note 
If the information you are searching for is not visible here, you can email me at dcsalina@go.olemiss.edu to find out more.
```{r, message = FALSE, echo=FALSE}
# dbDisconnect(ttrcon)
# dbDisconnect(ttrcon2)
```


<!-- ```{sql, connection = ttr_con}  -->
<!-- --SQL comment -->
<!-- SELECT *  -->
<!-- FROM transit_cost -->
<!-- WHERE State = 'Texas' -->
<!-- LIMIT 10 -->
<!-- ``` -->


