---
title: "What is Differential Privacy?"
output:
  html_document:
    df_print: paged
---
<style type="text/css">
.main-container {
  max-width: 1000px;
  margin-left: auto;
  margin-right: auto;
}

 /* unvisited link */
a:link {
  color: navy;
}

/* visited link */
a:visited {
  color: green;
}

/* mouse over link */
a:hover {
  color: purple;
}

/* selected link */
a:active {
  color: blue;
} 
</style>

Differential privacy (DP) is a system for publicly sharing information about a dataset by describing the patterns of groups within the dataset while still withholding information about individuals. As Wikipedia states:

<blockquote> 
Roughly, an algorithm is differentially private if an observer seeing its output cannot tell if a particular individual's information was used in the computation. Differential privacy is often discussed in the context of identifying individuals whose information may be in a database. Although it does not directly refer to identification and reidentification attacks, differentially private algorithms probably resist such attacks.
</blockquote>

<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}

 /* unvisited link */
a:link {
  color: navy;
}

/* visited link */
a:visited {
  color: green;
}

/* mouse over link */
a:hover {
  color: purple;
}

/* selected link */
a:active {
  color: blue;
} 
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-library, message=FALSE, echo=FALSE}
rm(list = ls())
pacman::p_load(tidyverse, rmarkdown, htmlwidgets, htmltools, maps, 
               webshot, leaflet, kableExtra, scales, stringr, stringi,
               mapproj, usmap, rvest, rcis, plotly, cowplot, socviz, 
               RColorBrewer, kableExtra, gridExtra, dplyr, tidyr, 
               ggplot2, diffpriv, sdcMicro, readr, ggrepel, randomNames)

suppressPackageStartupMessages({
  library(data.table)
  library(digest)
  library(knitr) # used only for post creation
})

library(tinytex) 
webshot::install_phantomjs(force=TRUE)
```

## Modification of Data {.tabset}
### Original Data
```{r ktable-1, warning=FALSE, message=FALSE}
#library(htmltools)
rawData <- read.csv("data/MockData4.csv")
data <- rawData

#original file is dat // changing the names 
dat <- rawData %>%
  rename("ID" = id) %>%
  rename("Name" = name) %>%
  rename("Email" = email) %>%
  rename("Gender" = gender) %>%
  rename("Age" = age) %>%
  rename("City" = city) %>%
  rename("State" = state) %>%
  rename("SSN" = ssn) %>%
  rename("Race/Ethnicity" = race) %>%
  rename("Diabetes" = diabetes) %>%
  rename("Asthma" = asthma) %>%
  rename("Depression" = depression) %>% 
  rename("Anxiety" = anxiety) %>%
  rename("Migraines" = migraines) %>%
  rename("Arthritis" = arthritis) %>%
  rename("Eczema" = eczema) %>%
  rename("Stroke" = stroke) %>%
  rename("Dementia" = dementia) %>%
  rename("HIV" = HIV) 

dat1 <- dat %>% 
  select(ID, Name, Email, Gender, Age, City, State, 
         SSN, `Race/Ethnicity`)

kable(head(dat1),caption = "Raw Data Table", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                bootstrap_options = "striped", full_width = FALSE, 
                position = "center")%>%
  row_spec(0, background = "lightblue", color= "black")
```

```{r binary-to-all, warning=FALSE, message=FALSE}
#library(htmltools)
####################### CHANGING THE INFORMATION TO 1/0 #######################
# Diabetes
data$diabetes [data$diabetes == "Yes"] <- 1
data$diabetes [data$diabetes == "No"] <- 0
data$diabetes <- as.character(data$diabetes)

# Asthma
data$asthma [data$asthma == "Yes"] <- 1
data$asthma [data$asthma == "No"] <- 0
data$asthma <- as.character(data$asthma)

# Depression
data$depression [data$depression == "Yes"] <- 1
data$depression [data$depression == "No"] <- 0
data$depression <- as.character(data$depression)

# Anxiety
data$anxiety [data$anxiety == "Yes"] <- 1
data$anxiety [data$anxiety == "No"] <- 0
data$anxiety <- as.character(data$anxiety)

# Migraines
data$migraines [data$migraines == "Yes"] <- 1
data$migraines [data$migraines == "No"] <- 0
data$migraines <- as.character(data$migraines)

# Arthritis
data$arthritis [data$arthritis == "Yes"] <- 1
data$arthritis [data$arthritis == "No"] <- 0
data$arthritis <- as.character(data$arthritis)

# Eczema
data$eczema [data$eczema == "Yes"] <- 1
data$eczema [data$eczema == "No"] <- 0
data$eczema <- as.character(data$eczema)

# Stroke
data$stroke [data$stroke == "Yes"] <- 1
data$stroke [data$stroke == "No"] <- 0
data$stroke <- as.character(data$stroke)

# Dementia
data$dementia [data$dementia == "Yes"] <- 1
data$dementia [data$dementia == "No"] <- 0
data$dementia <- as.character(data$dementia)

# HIV
data$HIV [data$HIV == "Yes"] <- 1
data$HIV [data$HIV == "No"] <- 0
data$HIV <- as.character(data$HIV)

ID <- data$id
Gender <- data$gender
Location <- data$state
Race <- data$race
```
<p>&nbsp;</p>

### Modified Data I 
```{r ktable-2, warning=FALSE, message=FALSE}
# columns which will be changed
willAnonymize <- c("email", "city")

# anonymize using the murmur32 algorithm 
anonymize <- function(x, algo="murmur32"){
  unq_hashes <- vapply(unique(x), function(object) digest(object, algo=algo), 
                       FUN.VALUE="", USE.NAMES=TRUE) #hashing for unique inputs
  unname(unq_hashes[x])
}

# columns which will be changed
willAnonymize2 <- c("name", "ssn")

# anonymize using the xxhash64 algorithm 
anonymize2 <- function(x, algo="xxhash64"){
  unq_hashes2 <- vapply(unique(x), function(object) digest(object, algo=algo), 
                       FUN.VALUE="", USE.NAMES=TRUE) #hashing for unique inputs
  unname(unq_hashes2[x])
}

data2 <- data # create a new dataframe from changed data of 1/0

# change age format --> re-coding the age to reduce uniqueness //
# generalization to achieve k-anonymity
data2$age <- cut(data$age, breaks = c(0, 21, 29, 39, 49, 59, 71, 100))

setDT(data2) #turning the dataframe into a data table to 
# be able to use the := function

# anonymize the data// run the dataset through the anonymize functions
data2[, (willAnonymize) := lapply(.SD, anonymize), .SDcols = willAnonymize]
data2[, (willAnonymize2) := lapply(.SD, anonymize2), .SDcols = willAnonymize2]

data2 <- data2 %>%
  rename("ID" = id) %>%
  rename("Name" = name) %>%
  rename("Email" = email) %>%
  rename("Gender" = gender) %>%
  rename("Age" = age) %>%
  rename("City" = city) %>%
  rename("State" = state) %>%
  rename("SSN" = ssn) %>%
  rename("Race/Ethnicity" = race) %>%
  rename("Diabetes" = diabetes) %>%
  rename("Asthma" = asthma) %>%
  rename("Depression" = depression) %>% 
  rename("Anxiety" = anxiety) %>%
  rename("Migraines" = migraines) %>%
  rename("Arthritis" = arthritis) %>%
  rename("Eczema" = eczema) %>%
  rename("Stroke" = stroke) %>%
  rename("Dementia" = dementia) %>%
  rename("HIV" = HIV) 

data2a <- data2 %>%
  select(ID, Name, Email, Gender, Age, City, State, SSN, 
         `Race/Ethnicity`)

kable(head(data2a),caption = "Modified table I", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                bootstrap_options = "striped", 
                full_width = FALSE, position = "center")%>%
  row_spec(0, background = "lightblue", color= "black")
```

<p>&nbsp;</p>

### Modified Data II
```{r ktable-3, warning=FALSE, message=FALSE}
# shuffle the dataframe by rows
shuffled_data = data2[sample(1:nrow(data2)), ]

shuffled_data1 <- shuffled_data %>%
  select(ID, Name, Email, Gender, Age, City, State, SSN, 
         `Race/Ethnicity`)

kable(head(shuffled_data1),caption = "Modified table II", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                bootstrap_options = "striped", 
                full_width = FALSE, position = "center")%>%
  row_spec(0, background = "lightblue", color= "black")
```

<p>&nbsp;</p>

### Modified Data III
```{r ktable-4, warning=FALSE, message=FALSE}
shuffled_data1b <- shuffled_data %>%
  select(Name, Email, Gender, Age, City, State, SSN, 
         `Race/Ethnicity`)

kable(head(shuffled_data1b),caption = "Modified table III", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                bootstrap_options = "striped", 
                full_width = FALSE, position = "center")%>%
  row_spec(0, background = "lightblue", color= "black")
```
<p>&nbsp;</p>

## The Average Percentage of Patients with [~] from the Dataset 
```{r mean-of-all, warning=FALSE, echo = FALSE}
# Getting the Mean for All
# turning the diagnoses data into vectors and (currently it is a character so) switching it to numeric
Diabetes <- data$diabetes %>%
  as.numeric()
Asthma <- data$asthma %>%
  as.numeric()
Depression <- data$depression %>%
  as.numeric()
Anxiety <- data$anxiety %>%
  as.numeric()
Migraines <- data$migraines %>%
  as.numeric()
Arthritis <- data$arthritis %>%
  as.numeric()
Eczema <- data$eczema %>%
  as.numeric()
Stroke <- data$stroke %>%
  as.numeric()
Dementia <- data$dementia %>%
  as.numeric()
HIV <- data$HIV %>%
  as.numeric()

DiabetesMean <- mean(Diabetes)
AsthmaMean <- mean(Asthma)
DepressionMean <- mean(Depression)
AnxietyMean <- mean(Anxiety)
MigrainesMean <- mean(Migraines)
ArthritisMean <- mean(Arthritis)
EczemaMean <- mean(Eczema)
StrokeMean <- mean(Stroke)
DementiaMean <- mean(Dementia)
HIVMean <- mean(HIV)

cat("Average for Diabetes: ", DiabetesMean, "\n")
cat("Average for Asthma: ", AsthmaMean, "\n")
cat("Average for Depression: ", DepressionMean, "\n")
cat("Average for Anxiety: ", AnxietyMean, "\n")
cat("Average for Migraines: ", MigrainesMean, "\n")
cat("Average for Arthritis", ArthritisMean, "\n")
cat("Average for Eczema", EczemaMean, "\n")
cat("Average for Stroke", StrokeMean, "\n")
cat("Average for Dementia", DementiaMean, "\n")
cat("Average for HIV", HIVMean, "\n")

```

```{r normal-distribution-noise, warning=FALSE, message=FALSE}
# noise from normal distribution
# now choosing an average of 10% to corrupt at random 
set.seed(1) # specified a seed to make my data reproducible//get the same numbers repeatedly
noise_20 <- rbinom(length(HIV), 1, 0.20) 
# corrupt at random generation the vector HIV, for -- trials, for probability 
# of 20% say Yes (1) vs No (0)// probability of success on each trial

#used binomial distribution since these are yes/no question-answers

set.seed(3)# specified a seed to make my data reproducible//get the same numbers repeatedly
noise_50 <- rbinom(length(HIV), 1, 0.50) 
# corrupt at random generation the vector HIV, for -- trials, for probability 
# of 50% say Yes (1) vs No (0)// probability of success on each trial


set.seed(4)# specified a seed to make my data reproducible//get the same numbers repeatedly
noise_80 <- rbinom(length(HIV), 1, 0.80) 
# corrupt at random generation the vector HIV, for -- trials, for probability 
# of 80% say Yes (1) vs No (0)// probability of success on each trial

# 
# ?Distributions
# x[corrupt] <- noise
# x <- as.numeric(x)
# x <- as.logical(x)
# HIV_noise <-as.data.frame(x)

```
<p>&nbsp;</p>

## Standard Deviations {.tabset}

Data density is important because it affects accuracy. Higher densities (not to be confused with higher standard deviations) mean more accuracy. Visually, we can see here how standard deviation affects the results we get. <b>Low standard deviation</b> means data is clustered around the mean, and <b>high standard deviation</b> indicates data are more spread out. A high standard deviation shows that the data is widely spread (less reliable) and a low standard deviation shows that the data are clustered closely around the mean (more reliable).

In other words, a standard deviation close to zero indicates that data points are close to the mean, whereas a high or low standard deviation indicates data points are respectively above or below the mean. 

### Original Data
```{r plotting-nd, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
# Plot the bar chart for the total in HIV 
countOfHIV <- data %>%
  count(HIV) 

countOfHIV %>%
ggplot(aes(x = HIV, y = n, fill = n)) + 
  geom_bar(stat = "identity", fill = "lightblue") +
  # geom_text(aes(label=n), vjust=2,size = 9, colour = "white") +
  labs(title = "HIV Results Total")

```
<p>&nbsp;</p>

### Standard Deviation of .2
```{r plotting-nd1, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
# rnorm(n, mean = , sd = )
# noisy_data <- signal + noise
# rnorm((noise),  )
noisy_data_20 <- HIV + rnorm((HIV), 0.172, .2)
# generate the noise to add and round it 

# Plot the histograms for the above 
hist(noisy_data_20, main = "Normal Distribution", 
     col = "lightblue", xlim = c(-5, 5), ylim = c(0, 1.6), freq = FALSE)

# vertical line // mean
abline(v=0.172,col="red",lwd=3)

# vertical line
abline(v=1,col="darkgreen",lwd=3)
```
<p>&nbsp;</p>

### Standard Deviation of .5
```{r plotting-nd2, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
# rnorm(n, mean = , sd = )
# noisy_data <- signal + noise
# rnorm((noise),  )
noisy_data_50 <- HIV + rnorm((HIV), 0.172, .5)
# generate the noise to add and round it 

hist(noisy_data_50, main = "Normal Distribution", 
     col = "lightblue", xlim =c(-5, 5), ylim = c(0, .8), freq = FALSE)

# vertical line
abline(v=0.172,col="red",lwd=3)

# vertical line
abline(v=1,col="darkgreen",lwd=3)
```
<p>&nbsp;</p>

### Standard Deviation of .75
```{r plotting-nd3, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
# rnorm(n, mean = , sd = )
# noisy_data <- signal + noise
# rnorm((noise),  )
noisy_data_80 <- HIV + rnorm((HIV), 0.172, .75)
# generate the noise to add and round it 

hist(noisy_data_80, main = "Normal Distribution",
     col = "lightblue", xlim = c(-5, 5), ylim = c(0, .5), freq = FALSE)

# vertical line
abline(v=0.172,col="red",lwd=3)

# vertical line
abline(v=1,col="darkgreen",lwd=3)

```
<p>&nbsp;</p>

## Adding Noise to the Data 
```{r noise-nd-1, warning=FALSE, message=TRUE, echo = TRUE}
x_20 <- HIV # HIV vector, calling it to x
print(x_20, max=500)

# adding noise to 10% percent of the data
x_noise_20 <- sample(0:1, 200,replace=TRUE)  
print(x_noise_20)

# about 10% of x has been corrupted // the first 100 values
x_20[1:200] <- c(x_noise_20) 
print(x_20, max=500)

x_20 <- x_20 %>%
  as.character()

HIVtibble2D <- tibble(ID, Gender, Location, Race, x_20)

HIVtibble2D <- HIVtibble2D %>%
  rename("HIV Results with Noise - 20" = x_20)
  
HIVtibble2Da <- HIVtibble2D %>%
  group_by(Location) %>%
  count(`HIV Results with Noise - 20`)
```
```{r noise-nd-2, warning=FALSE, message=FALSE, echo = FALSE}


x_50 <- HIV # HIV vector, calling it to x

# adding noise to 50% percent of the data
x_noise_50 <- sample(0:1, 500,replace=TRUE)  

# about 50% of x has been corrupted // the first 500 values
x_50[1:500] <- c(x_noise_50) 

x_50 <- x_50 %>%
  as.character()

HIVtibble3 <- tibble(ID, Gender, Location, Race, x_50)

HIVtibble3 <- HIVtibble3 %>%
  rename("HIV Results with Noise - 50" = x_50)
  
HIVtibble3a <- HIVtibble3 %>%
  group_by(Location) %>%
  count(`HIV Results with Noise - 50`)
```

```{r noise-nd-3, warning=FALSE, message=FALSE, echo = FALSE}
x_75 <- HIV # HIV vector, calling it to x

# adding noise to 75% percent of the data
x_noise_75 <- sample(0:1, 750,replace=TRUE)  

# about 75% of x has been corrupted // the first 750 values
x_75[1:750] <- c(x_noise_75) 

x_75 <- x_75 %>%
  as.character()

HIVtibble4 <- tibble(ID, Gender, Location, Race, x_75)

HIVtibble4 <- HIVtibble4 %>%
  rename("HIV Results with Noise - 75" = x_75)

HIVtibble4a <- HIVtibble4 %>%
  group_by(Location) %>%
  count(`HIV Results with Noise - 75`)
```

```{r tibble-HIVnoise-1, warning=FALSE, message=TRUE, echo = FALSE}
######################### CREATING TIBBLE FOR HIV ###########################
HIV <- HIV %>%
  as.character()
x_20 <- x_20 %>%
  as.character()

HIVtibble <- tibble(ID, Gender, Location, Race,HIV, x_20)

HIVtibble <- HIVtibble %>%
  rename("HIV Results" = HIV) %>%
  rename("HIV Results with Noise" = x_20)
  
HIVtibble1 <- HIVtibble %>%
  group_by(Location) %>%
  count(`HIV Results`)

HIVtibble2 <- HIVtibble %>%
  group_by(Location) %>%
  count(`HIV Results with Noise`)
```
<p>&nbsp;</p>

## Positive Cases Map Visualization {.tabset}
### Orignal Data 
```{r visualizing0, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
# joining the data
us_states <- us_map("state") %>%
  rename("long" = x) %>%
  rename("lat" = y) %>%
  rename("state" = abbr) %>%
  rename("Location" = full)

HIVtibble5 <- HIVtibble %>%
  group_by(Location) %>%
  count(`HIV Results`)

mapToBeUsedForHIV1 <- left_join(us_states, HIVtibble5, by="Location")

mapToBeUsedForHIV1 %>%
  ggplot(mapping = aes(x = long, y = lat, group = group, fill = n)) +
  geom_polygon(color = "gray", linewidth=0.2) +
  coord_equal() +
  labs(title = "HIV Results without Noise",
       subtitle = "Diana Salinas")+
  scale_fill_distiller(palette = "Blues", trans = "reverse") +
  theme_map() 
```
<p>&nbsp;</p><p>&nbsp;</p>

### 20% 
```{r visualizing1, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
# joining the data
mapToBeUsedForHIV2 <- left_join(us_states, HIVtibble2, by="Location")

mapToBeUsedForHIV2 %>%
  ggplot(mapping = aes(x = long, y = lat, group = group, fill = n)) +
  geom_polygon(color = "gray", linewidth=0.2) +
  coord_equal() +
  labs(title = "HIV Results with Noise",
       subtitle = "Diana Salinas")+
  scale_fill_distiller(palette = "Blues", trans = "reverse") +
  theme_map() 
```
<p>&nbsp;</p><p>&nbsp;</p>

### 50% 
```{r visualizing2, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
# joining the data
mapToBeUsedForHIV3 <- left_join(us_states, HIVtibble3a, by="Location")

mapToBeUsedForHIV3 %>%
  ggplot(mapping = aes(x = long, y = lat, group = group, fill = n)) +
  geom_polygon(color = "gray", linewidth=0.2) +
  coord_equal() +
  labs(title = "HIV Results with Noise",
       subtitle = "Diana Salinas")+
  scale_fill_distiller(palette = "Blues", trans = "reverse") +
  theme_map() 
```
<p>&nbsp;</p><p>&nbsp;</p>
### 75% 
```{r visualizing3, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
# joining the data
mapToBeUsedForHIV4 <- left_join(us_states, HIVtibble4a, by="Location")

mapToBeUsedForHIV4 %>%
  ggplot(mapping = aes(x = long, y = lat, group = group, fill = n)) +
  geom_polygon(color = "gray", linewidth=0.2) +
  coord_equal() +
  labs(title = "HIV Results with Noise",
       subtitle = "Diana Salinas")+
  scale_fill_distiller(palette = "Blues", trans = "reverse") +
  theme_map() 
```
<p>&nbsp;</p><p>&nbsp;</p>

## Comparison Data Tables {.tabset}
### Original Data
```{r graphing-HIV-no-noise-1, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
HIVtibble1 %>%
  ggplot(mapping = aes(x=Location,
                     y=n,
                     fill = `HIV Results`)) +
   geom_bar(position="dodge", stat="identity", reverse = TRUE) +
   ylim(0, 100) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
   scale_fill_discrete(labels=c('Negative', 'Positive')) +
  labs(title = "HIV Results without Noise", fill="Results")
```
<p>&nbsp;</p>


### MD 20%
```{r graphing-HIVnoise-2, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
HIVtibble2 %>%
  ggplot(mapping = aes(x=Location,
                     y=n,
                     fill = `HIV Results with Noise`)) +
   ylim(0, 100) +
   geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
   scale_fill_discrete(labels=c('Negative', 'Positive')) +
  labs(title = "HIV Results with Noise", fill="Results")
```

<p>&nbsp;</p>

### MD 50%
```{r graphing-HIVnoise-3, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
HIVtibble3a %>%
  ggplot(mapping = aes(x=Location,
                     y=n,
                     fill = `HIV Results with Noise - 50`)) +
   ylim(0, 100) +
   geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
   scale_fill_discrete(labels=c('Negative', 'Positive')) +
  labs(title = "HIV Results with Noise", fill="Results")
```

<p>&nbsp;</p>

### MD 75%
```{r graphing-HIVnoise-4, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
HIVtibble4a %>%
  ggplot(mapping = aes(x=Location,
                     y=n,
                     fill = `HIV Results with Noise - 75`)) +
   ylim(0, 100) +
   geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
   scale_fill_discrete(labels=c('Negative', 'Positive')) +
  labs(title = "HIV Results with Noise", fill="Results")
```
<p>&nbsp;</p>

## Separated Data Between Positive and Negative {.tabset}
### Original Data
```{r graphing-HIV-no-noise-1a, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
HIVtibble1 %>%
  ggplot(mapping = aes(x=Location,
                     y=n,
                     fill = `HIV Results`)) +
   geom_bar(position="dodge", stat="identity") +
   ylim(0, 100) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_text(aes(label=n), colour = "black", vjust=-.5,size = 4) +
  scale_fill_discrete(labels=c('Negative', 'Positive')) +
  labs(title = "HIV Results without Noise", fill="Results") +
  facet_wrap(~`HIV Results`, 2)
```

<p>&nbsp;</p>

### 20%
```{r graphing-HIV-noise-1a, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
HIVtibble2 %>%
  ggplot(mapping = aes(x=Location,
                     y=n,
                     fill = `HIV Results with Noise`)) +
   geom_bar(position="dodge", stat="identity") +
   ylim(0, 100) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_text(aes(label=n), colour = "black", vjust=-.5,size = 4) +
  scale_fill_discrete(labels=c('Negative', 'Positive')) +
  labs(title = "HIV Results with Noise", fill="Results") +
  facet_wrap(~`HIV Results with Noise`, 2)
```
<p>&nbsp;</p>

### 50%
```{r graphing-HIV-noise-2a, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
HIVtibble3a %>%
  ggplot(mapping = aes(x=Location,
                     y=n,
                     fill = `HIV Results with Noise - 50`)) +
   geom_bar(position="dodge", stat="identity") +
   ylim(0, 100) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_text(aes(label=n), colour = "black", vjust=-.5,size = 4) +
  scale_fill_discrete(labels=c('Negative', 'Positive')) +
  labs(title = "HIV Results with Noise", fill="Results") +
  facet_wrap(~`HIV Results with Noise - 50`, 2)
```
<p>&nbsp;</p>

### 75%
```{r graphing-HIV-noise-3a, warning=FALSE, message=TRUE, echo = FALSE, fig.width=14,fig.height=6}
HIVtibble4a %>%
  ggplot(mapping = aes(x=Location,
                     y=n,
                     fill = `HIV Results with Noise - 75`)) +
   geom_bar(position="dodge", stat="identity") +
   ylim(0, 100) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_text(aes(label=n), colour = "black", vjust=-.5,size = 4) +
  scale_fill_discrete(labels=c('Negative', 'Positive')) +
  labs(title = "HIV Results with Noise", fill="Results") +
  facet_wrap(~`HIV Results with Noise - 75`, 2)
```
<p>&nbsp;</p>

## How Can it be Improved
